Implicit yaddayadda

### 2011-10-26 papers/PLDI2012/implicitization.tex
temps d'exécution
reponse a un commentaire
ordre des mots + lisible

In such an analysis, information may flow forward (one computes the polyhedron after a program statement as the image, or a super-set thereof, of the polyhedron before by the semantics of the statement) or backward;
forward program analysis computes super-sets of the states reachable from the initialization of the program, backward program analysis computes super-sets of the states co-reachable from some property of interest (for instance, the violation of an assertion).
In forward analysis, control-flow joins correspond to computation of convex hulls if using convex polyhedra (more generally, they correspond to least upper bounds in a lattice); in backward analysis, it is control-flow splits.

>>>>

In such an analysis, information may flow forward (one computes the polyhedron after a program statement as the image by the semantics of the statement, or a super-set thereof, of the polyhedron before) or backward;
forward program analysis computes super-sets of the states reachable from the initialization of the program, backward program analysis computes super-sets of the states co-reachable from some property of interest (for instance, the violation of an assertion).
In forward analysis, control-flow joins correspond to computation of convex hulls if using convex polyhedra (more generally, they correspond to least upper bounds in a lattice); in backward analysis, it is control-flow splits.
